Enhancement of Speech Recognition Results Using Server-side Post-processing

### 2019-06-23 none_cloud_post_processing_decoding/doc/main.tex
Updates the paper

\title{A state of the art end-to-end speech recognition algorithm with
a homogenous structure.}

@@

@@

@@

In this section, we review well-known {\it sequence-to-sequence} algorithms
used in speech recognition.
\cite{
j_chorowski_nips_2015_00, 
a_graves_corr_2012_00, 
y_he_icassp_2019_00,
r_prabhavalkar_interspeech_2017_00}. 
A {\it sequence-to-sequence}
speech recognizers maps a sequence of input acoustic features into a sequence 
of text labels  \cite{r_prabhavalkar_interspeech_2017_00}. 
Mathematically, this model is 
represented by the following transformation $\mathcal{T}$ 
\cite{a_graves_icml_2006_00}:
\begin{align}
  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
	\label{eq:transformation}
\end{align}
where the symbol ${*}$ denotes a sequence, $d$ is the dimension of the input 
feature. $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
labels, which may be graphemes 
\cite{j_chorowski_nips_2015_00,
w_chan_icassp_2016_00},
subword units \cite{
a_zeyer_interspeech_2018_00,
c_chiu_icassp_2018_00},
 and words \cite{h_soltau_interspeech_2017_00}.
Let us denote a sequence of input acoustic feature vectors by 
$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels in 
{\it one-hot vector} representation or its label-smoothed 
representation \cite{} by 
$\mathcal{Y}_{0}^{L-1}$ as shown below:
\begin{subequations}
  \begin{align}
    \mathcal{X}[0:M]  =  
      \left\{\vec{x}[m]
          \Big| 0 \le m \le M - 1, \; \vec{x}[m] \in \mathbb{R}^d \right\},  
    \label{eq:input_seq} \\
    \mathcal{Y}_{0:L}  =  
      \left\{\vec{y}_l  \Big| 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
    \label{eq:target_label}
  \end{align}
\end{subequations}
where $M$ is the number of frames in the input feature sequence,
$L$ is the number of labels in the output target sequence,
 and $\mathbb{V}$ in \eqref{eq:target_label} is the set of outputs.
Note that the sequence index in \eqref{eq:input_seq} is a frame
index ({\it represented by} [m]), 
whereas the sequence index in \eqref{eq:target_label} is 
a label index ({\it represented by a subscript} $l$). 
Depending on whether the neural network generates
the inference output for every frame or not, there are following
categories:

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.35\textwidth}
    \centering
    \resizebox{23mm}{!}{
      \input{../figures/ctc_diagram.tex}
    } 
    \caption {
      Connectionist Temporal Classification (CTC) Model.
      \label{fig:ctc_diagram}
    }
  \end{subfigure}
  \begin{subfigure}[b]{0.60\textwidth}
    \centering
    \resizebox{78mm}{!}{
      \input{../figures/rnn_t_diagram.tex}
    }
    \caption {
      RNN-T Model.
      \label{fig:rnn_t_diagram}
    }
  \end{subfigure}

  \begin{subfigure}[b]{0.55\textwidth}
    \centering
    \resizebox{53mm}{!}{
      \input{../figures/attention_diagram.tex}
    }
    \caption {
      Attention-based Model.
      \label{fig:attention_diagram}
    }
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \resizebox{26mm}{!}{
      \input{../figures/fsc_diagram.tex}
    }
    \caption {
      Feedback Sequence Classifier (FSC) Model.
      \label{fig:fsc_diagram}
    }
  \end{subfigure}
  \caption{
    Comparison of block diagrams of different sequence-to-sequence speech
    recognition approaches.
    The proposed Feedback Sequence Classifier (FSC) is shown in 
    Fig. \ref{fig:fsc_diagram}.
  }

@@

\begin{figure}
  \centering
    \resizebox{100mm}{!}{
      \input{../figures/path_alignment.tex}
    } 
    \caption {
      An example of a path $\mathcal{Z}[0:M]$ and the path movement 
      constraint shown by dashed arrows $P \rightarrow Q$ and $P \rightarrow R$. 
      \label{fig:path_alignment}
    }
  \label{fig:path_alignment}
\end{figure}

@@

\begin{algorithm}
  \caption{$N$-best alignment algorithm}
  \begin{algorithmic}

  \Require {$\mathcal{X}[0:M]$}
  \Require {$\mathcal{Y}_{0:L}$}
  \Require {The neural network parameter $\Theta^{\left(i\right)}$ 
    for calculating 
      $p\left(\vec{z}[m] \big|
      \mathcal{Z}[0:m], \mathcal{X}[0:m+1]\right)$}

  \State {\textbf{Initialization:}}
  \State {Let $\mathcal{Z}_0[0:1] := \left\{ \vec{y}_0 \right\}  $}
  \State {Let $\mathcal{L}_{0} := \ln \left[ 
        p \left(\vec{y}_{0} \big| 
            {\mathcal{X}}[0:1]\right)  \right]$}
  \State {$\mathcal{Z}_b[0:1], 1 \le b < N_b$ are undefined.}
  \For {$m = 1, . . . , M-1$}
    \For {$b = 0, . . . , N_b-1$}
      \If {$\mathcal{Z}_{b}[0:m]$ is defined}
        \State {Let $\vec{y}_u := \vec{z}_{b}[m-1] $}
        \State {Let $\mathcal{Z}_{b, 0}[0:m+1] := \mathcal{Z}_{b}[0:m] 
                \cup \left\{ \vec{y}_u  \right\}  $} 
            \Comment {A horizontal move $P \rightarrow Q$ in 
            Fig. \ref{fig:path_alignment}}.
        \State {
              $\mathcal{L}_{b,0} := \ln \left[ 
                  p \left(\vec{y}_{u} \big| 
                      \mathcal{Z}_b[0:m], 
                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right]
                  + \mathcal{L}_b$}

        \If {$u+1 \le  L - 1$}
          \State {Let $\mathcal{Z}_{b, 1}[0:m+1] 
          := {\mathcal{Z}}_{b}[0:m] \cup \left\{ \vec{y}_{u+1}  \right\}  $} 
              \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
          \State  {
              $\mathcal{L}_{b,1} := \ln \left[ 
                  p \left(\vec{y}_{u+1} \big| 
                      \mathcal{Z}_b[0:m], 
                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right] 
                          + \mathcal{L}_b$}
      \EndIf
      \EndIf
    \EndFor
    \State {Sort a list of items
    $\left\{\mathcal{L}_{b, i}, {\mathcal{Z}}_{b, i}[0:m+1] \right\}, \; 0 \le
    b < N_b, i = 0, 1$ 
    with respect to the log likelihood $\mathcal{L}_{b, i}$ 
    in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
    follows: 
    $\left\{\mathcal{L}_{b}, \mathcal{Z}_{b}[0:m+1] \right\}$, $0 \le b < N_b$}
    where the first item in the sorted list is re-indexed to $b=0$, 
    the second item is re-indexed to $b=1$, and so on.
  \EndFor
  \label{algorithm:n_best_alignment}
  \end{algorithmic}
\end{algorithm}

>>>>

\title{Enhancement of Speech Recognition Results Using Server-side
Post-processing}

@@

\section{Introduction}

\section{Review on frame-synchronous speech recognition}

Let us suppose that the sequence of the text stream is $T$  
\begin{align}
  X
\end{align}

A speech recognizers maps a sequence of input acoustic features into a sequence 
of text labels  \cite{r_prabhavalkar_interspeech_2017_00}. 
Mathematically, this model is 
represented by the following transformation $\mathcal{T}$ 
\cite{a_graves_icml_2006_00}:
\begin{align}
  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
	\label{eq:transformation}
\end{align}
where the symbol ${*}$ denotes a sequence, $d$ is the dimension of the input 
feature. $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
labels, which may be graphemes 
\cite{j_chorowski_nips_2015_00,
w_chan_icassp_2016_00},
subword units \cite{
a_zeyer_interspeech_2018_00,
c_chiu_icassp_2018_00},
 and words \cite{h_soltau_interspeech_2017_00}.

\section{The structure of the Server-side Post Processing System}

Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
system and the server-side post processing system. 
The symbols used in this figure is defined as follows:
%
\begin{align}
  \vec{x}[m]:& \quad \text{Acoustic feature vector from speech.}  \nonumber \\
  \hat{y}_o[l]:& \quad \text{The frame-synchronous hypothesis from the
  on-device speech recognizer.}   \nonumber \\
       & \quad \hat{y}_o[l] \in \mathbb{V}.  \nonumber \\
  \hat{y}_o[0:l+1]  : & \quad \text{The sequence of $y[l']$ where } 0 \le l'
  \le l. \quad  \hat{y}_o[l'] \in \mathbb{V}.  \nonumber \\ 
  \hat{y}_p[l]:& \quad \text{The frame-synchronous hypothesis for post-processing.}
  \quad \hat{y}_p[l] \in \mathbb{V}.   \nonumber \\
  W_i: & \quad \text{The word sequence. } W_i \in  \mathbb{D}.  \nonumber 
\end{align}
where $\mathbb{V}$ is the set of grapheme symbols, and $\mathbb{D}$ is the
set of words. In Fig. \ref{fig:entire_system}, there are two top level
blocks. The left and right blocks correspond to processing on the local
device and the server side post processing respectively.

\subsection{Label Likelihood Calculation}
To perform decoding described in Section \ref{sec:decoding}, 
we need to calculate likelihood $P(y[0:l+1] |z[l])$
where $\mathcal{Y}[0:l]$ is the 
In this block, the objective is to calculate the likelihood
of the on-device ASR output $\mathcal{Y}[0:l]$ depending on 
the label $z[l]$, which may be mathematically given
by
\begin{align}
  P(\hat{y}_o[0:l+1] \big| \hat{y}_p[l]) 
    = \frac{P(\hat{y}_p[l] \big| \hat{y}_o[0:l+1])
        P\left(\hat{y}_o[0:l+1] \right)}{P(\hat{y}_p[l])}
  \label{eq:post_prob}
\end{align}

\subsection{Decoding}
\label{sec:decoding}
The structure of the post-processing decoder is depicted in Fig.
\ref{post_processing_decoder}. Using the dictionary and the
language model, the hypothesis word sequence $W_i$ is obtained
from the posterior probability in \eqref{eq:post_prob}.

\begin{figure}
  \centering
    \centering
    \resizebox{130mm}{!}{
      \input{../figures/hybrid_on_device_cloud_asr.tex}
    }
    \caption {
      The structure of an entire system consisting of the on-device speech 
      recognition and the server-side post processing. 
      \label{fig:entire_system}
    }
\end{figure}

\begin{figure}
  \centering
    \centering
    \resizebox{55mm}{!}{
      \input{../figures/asr_system.tex}
    }
    \caption {
      The on-device Automatic Speech Recognition (ASR) system.
      \label{fig:asr_system}
    }
\end{figure}

\begin{figure}
    \centering
    \resizebox{30mm}{!}{
      \input{../figures/label_posteior_prob_estimation.tex}
    } 
    \caption {
      Estimation of the label posterior probability
      \label{fig:label_posterior_prob_estimation}
    }
\end{figure}

\begin{figure}
    \centering
    \resizebox{70mm}{!}{
      \input{../figures/post_processing_decoder.tex}
    } 
    \caption {
      The post-processing decoder for generating the word sequence $W_i$
      from the label likelihood $P(\hat{y}_o[0:l+1] | \hat{y}_p[l])$ in \eqref{eq:post_prob}, 
      using the dictionary and the language model.
      \label{fig:post_processing_decoder}
    }
\end{figure}

@@

In this section, we review well-known {\it sequence-to-sequence} algorithms
used in speech recognition.
\cite{
j_chorowski_nips_2015_00, 
a_graves_corr_2012_00, 
y_he_icassp_2019_00,
r_prabhavalkar_interspeech_2017_00}. 
where $M$ is the number of frames in the input feature sequence,
$L$ is the number of labels in the output target sequence,
 and $\mathbb{V}$ in \eqref{eq:target_label} is the set of outputs.
Note that the sequence index in \eqref{eq:input_seq} is a frame
index ({\it represented by} [m]), 
whereas the sequence index in \eqref{eq:target_label} is 
a label index ({\it represented by a subscript} $l$). 
Depending on whether the neural network generates
the inference output for every frame or not, there are following
categories:

@@

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.60\textwidth}
    \centering
    \resizebox{78mm}{!}{
      \input{../figures/rnn_t_diagram.tex}
    }
    \caption {
      RNN-T Model.
      \label{fig:rnn_t_diagram}
    }
  \end{subfigure}

  \begin{subfigure}[b]{0.55\textwidth}
    \centering
    \resizebox{53mm}{!}{
      \input{../figures/attention_diagram.tex}
    }
    \caption {
      Attention-based Model.
      \label{fig:attention_diagram}
    }
  \end{subfigure}
  \caption{
    Comparison of block diagrams of different sequence-to-sequence speech
    recognition approaches.
    The proposed Feedback Sequence Classifier (FSC) is shown in 
    Fig. \ref{fig:fsc_diagram}.
  }

@@

@@
